Local to Global Mariculture Modelling

### 2025-07-30 index.qmd
Latitude sorting of countries

farm_locs <- find_read(output_farm_data_path, "geometry") %>% 
  rename(farm_ID = farm_id)
```

>>>>

farm_locs <- find_read(output_farm_data_path, "geometry") %>% 
  rename(farm_ID = farm_id)

farm_mean_lat <- farm_locs %>%
  st_centroid() %>%
  mutate(latitude = st_coordinates(.)[, "Y"]) %>%
  st_drop_geometry() %>%
  group_by(country) %>%
  summarise(mean_latitude = mean(latitude, na.rm = TRUE)) %>% 
  arrange(-mean_latitude)

countries <- farm_mean_lat$country
countries[str_detect(countries, "United States of America")] <- "USA"
countries[str_detect(countries, "United Kingdom")] <- "UK"
countries[str_detect(countries, "Russian Federation")] <- "Russia"

farm_locs <- farm_locs %>% 
  mutate(country = factor(country, levels = farm_mean_lat$country, labels = countries))
```
